\documentclass{article}
\usepackage{scimisc-cv}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\title{Scismic's Recommended CV for Biotech and Pharma Positions}
\author{Scismic: The Talent Matching Platform for The Life Sciences (www.scismic.com)}
\date{May 2020}

%% These are custom commands defined in scimisc-cv.sty
\cvname{Harsh Pranav Patel}
\cvpersonalinfo{
harsh.p@dal.ca \cvinfosep
+1 (902)9891532 \cvinfosep
\href{https://harshp.tech/}{harshp.tech/} \cvinfosep
\href{https://github.com/Harshpatel249}{GitHub} \cvinfosep
\href{https://www.linkedin.com/in/harsh-patel-696a82176/}{\textcolor{blue}{LinkedIn}}
}

\begin{document}

% \maketitle %% This is LaTeX's default title constructed from \title,\author,\date

\makecvtitle %% This is a custom command constructing the CV title from \cvname, \cvpersonalinfo

\section{Education}
\begin{itemize}

\item
\cvsubsection{Dalhousie University}[Expected August 2024]
\textit{Masters of Applied Computer Science}
\\
CGPA: 4.3/4.3
\item
\cvsubsection{School of Engineering and Applied Science, Ahmedabad University}[June 2022]
\textit{Bachelor of Technology in Information and Communication Technology}


\end{itemize}
 
\section{Technical Skills}

\begin{itemize}
\item \textbf{Programming Languages:} C, C++, JAVA, Dart, JavaScript (ES5/ES6), TypeScript, LaTex
\item \textbf{Database Systems:} SQL Server, MongoDB, FireStore, DynamoDB
\item \textbf{Web Technologies:} React.js, Angular, Node.js, Express.js, Flutter (Dart), Tailwind CSS, Chakra UI
\item \textbf{Cloud Technologies:} Amazon Web Services, Google Cloud Platform
\item \textbf{Project Management:} Software Development Life Cycle, Agile, Scrum, CI/CD, Git  
\item \textbf{Others:} Docker, Firebase, Netlify, Data Structures and Algorithms, MVC pattern, Postman

\end{itemize}

\section{Certifications}
\begin{itemize}
\item \textbf{AWS Cloud Practitioner}
\item \textbf{CISEH: Certified in Ethical Hacking and Information Security}
\end{itemize}


\section{Work Experience}

\cvsubsection{Full-Stack Developer Intern \\ Quicko Infosoft Pvt Ltd (6 Months)\hspace{11cm}Dec'21 to June'22}[]
\begin{itemize}
    \item Developed 3 different Progressive Web Apps as the lead developer for the product "MEET".
    \item Increased the user conversion rate by 65\% by ideating and implementing a new workflow with improved funnels.
    \item Decreased the order life-cycle from a maximum 1 week long duration to 1 hour per order by developing a new and revised order workflow.
    \item Developed and integrated over 100 API calls with 3 different UI workflows.\\
\textbf{Technologies:} Flutter, Node.js, Angular, JAVA services, AWS 

\end{itemize}

% \cvsubsection{Teaching Assistant  \\ Ahmedabad University (Aug'21 to Dec'21)}[]
% \begin{itemize}
%     \item Helped a batch of 120 students with their Embedded Systems Design course as a Teaching Assistant/Marker at Ahmedabad University.
%     \item Conducted the laboratory sessions for the course as the primary instructor and helped the students with implementing their lab assignments.
%     \item Assisted the students in ideating and building their project.
% \end{itemize}

% \cvsubsection{FullStack Web Developer Intern \\ Growth Central VC (3 Months)(Aug'21 to October'21)}[]
% \begin{itemize}
%     \item \\
% \textbf{Technologies used:} MongoDB, Express.js, ReactJS, Node.js

% \end{itemize}

\cvsubsection{Flutter Developer Intern \\ Ahmedabad University (3 Months)\hspace{11cm}May'21 to July'21}[]
\begin{itemize}
    \item Created an application with the features identified by 12 months long research on mental health.
    \item Research observed that intentionally laughing 2-3 times a day improved the individual's mental health greatly.
    \item Application kept track of user's daily sessions, sent reminders and provided laugh along videos from the community.\\
\textbf{Technologies:} Flutter, Dart, FireStore, Firebase
\end{itemize}

% \cvsubsection{Driver-Pedestrian Interaction Research Internship \\ Ahmedabad University (2 Months)(June'21 to July'21)}[]
% \begin{itemize}
%     \item Created a data-set from over 500 hours of dash-cam footage captured in the city of Ahmedabad, India for using in Intelligent Transportation Systems.
%     \item Extracted over 600 meaningful interactions between the driver and a pedestrian to include into the data-set.
%     \item The data-set was annotated with 14 different attributes for documenting driver-pedestrian interactions. \\
% \textbf{Tags:} Research, Deep Learning

% \end{itemize}



 
\section{Projects}

%% Another custom command provide by scimisc-cv.sty.
%% First two argumetns are typeset on the first line in bold; 3rd and 4th arguments are typset on second line in italics. 2nd, 3rd and 4th arguments are OPTIONAL

\cvsubsection{
\href{https://tune-hub.netlify.app/}{TuneHub: IMDb for music} 
\hspace{13.5cm}
\href{https://github.com/Harshpatel249/web-project}{GitHub}}[] 

\begin{itemize}
\item Implemented more than 7 different features along with the reviews and rating system.
\item Integrated with Spotify Developer apis to provide 4 user metrics.
\item Used UI/UX principles for the website design and ChakraUI for React components.

\end{itemize}

\textbf{Technologies:} React.js, Chakra-UI, Node.js, Express.js, MongoDB, Netlify, Render and Gitlab pipelines

\cvsubsection{
\href{https://commune-dev-csci5308-group06.netlify.app/}{Commune: A community-event management system} 
\hspace{9.5cm}
\href{https://github.com/Harshpatel249/asdc-project}{GitHub}}[] 

\begin{itemize}
\item Created the community module consisting of more than 20 api end-points.
\item Designed and connected more than 25 RESTful API endpoints with the front-end.
\item Used Test-Driven development with Springboot for backend.

\end{itemize}

\textbf{Technologies:} React.js, Chakra-UI, JAVA, SpringBoot, MySQL, Netlify, Render and Gitlab pipelines


\cvsubsection{
\href{https://main--serverless-sdp8-production.netlify.app/}{FoodVaganza: A restaurant booking application} 
\hspace{10.3cm}
\href{https://github.com/dev-patel2104/ServerlessSDP8}{GitHub}}[] 

\begin{itemize}
\item Launched three different apps: customer app, partner app and admin app.
\item Designed over 20 independent FaaS AWS lambdas served using AWS API Gateway.
\item Entire backend was implemented on a serverless architecture using AWS Lambdas, GCP cloud functions, AWS API gateway, AWS DynamoDB, GCP Firestore.

\end{itemize}

\textbf{Technologies:} React.js, Chakra-UI, AWS EC2, AWS Node.js Lambdas, GCP Node.js cloud functions, DynamoDB, Firestore


\cvsubsection{
\href{https://app-lify.netlify.app/}{Applify: Minimalist job application tracker} 
\hspace{11cm}
\href{https://github.com/Harshpatel249/applify}{GitHub}}[] 

\begin{itemize}
\item Entire application deployable using AWS CloudFormation.
\item Minimalistic front-end design working with 7 api endpoints.
\item Backend supports 2 architectures: serverless and serverful architecture.

\end{itemize}

\textbf{Technologies:} React.js, Chakra-UI, AWS EC2, AWS Node.js Lambdas, DynamoDB, MongoDB, ExpressJS, Render, Netlify
% \cvsubsection{
% \href{https://github.com/Harshpatel249/CorVito}{CorVito - Movie recommendation/watchlist website}
% }[]
% \begin{itemize}
% \item Developed an interactive website and movie recommendation ML model using HCI principles and GMMs.
% \item Used ReactJS with Material UI components to develop user-friendly design and workflow.
% \item Users watchlist is fed into the machine learning model for clustering and generating movie recommendations.
% \end{itemize}
% \textbf{Technologies used:} React.js, Material UI


% \cvsubsection{
% \href{https://github.com/Harshpatel249/Echos}{Echos: American Sign Language Tutor and ASL to Text translator [Led a team of 8]}
% }[]
% \begin{itemize}
% \item An app like Duolingo with more than 25 video tutorials and related quiz content inside the app to teach the users American Sign Language (ASL).
% \item A bonus feature that uses camera feed and deep learning model to convert all the 26 alphabets from ASL to English text.
% \item Agile methodology was used for the development with 2 week long sprints with CI/CD.
% \end{itemize}
% \textbf{Technologies used:} 
% Front-end: Flutter (Dart) | Back-end: Firebase | Machine Learning: NumPy, TensorFlow, Keras

%% An example of leaving an argument empty

% \section{Other Skills/Interests}
% \begin{description}[widest=Langauges]
% \item[Software]     Adobe premier pro
% \item[Interests] Competitive Programming, portrait sketching, video games, guitar, volleyball
% \end{description}


\end{document}